\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-25 paper/main.tex
Update significance test results reporting

As the difference in performance with different splitting schemes is
quite large, we further evaluated additional drug--target interaction
and drug--target affinity prediction methods that were trained and
evaluation on other datasets.  Following the results of MolTrans
\cite{MolTrans2020}, we reevaluated DeepDTI \cite{DeepDTI2017},
DeepDTA \cite{DeepDTA2018}, DeepConv-DTI \cite{DeepConvDTI2019}, and
MolTrans itself on the BioSnap dataset \cite{BioSnap2018} and compared it to our
``na\"ive'' predictor as well as \name{} (see Table
\ref{tab:comparison2}).  MolTrans was evaluated over the drug--target
pair and the protein split; we were able to reproduce the MolTrans
results (Table \ref{tab:comparison2}), showing a substantial
difference based on the splitting scheme. We additionally computed the
$MicroAUC_p$ score for all considered methods, leading to similar 
results as observed on the Yaminishi dataset. As \name{} considers less drugs than alternative approaches, we execute a one-tailed T-test with $\alpha=0.01$ over all considered methods. Considering Macro AUCs, \name{} improves significantly over MolTrans ($p<0.0001$), DeepDTI ($p<0.0001$), DeepDTA ($p<0.0001$), and DeepConv-DTI ($p<0.0001$) with respect to BioSnap dataset, and significantly over DTINet ($p<0.0001$) and DTIGEMS+ ($p<0.0001$) with respect to Yamanishi dataset. However, DTI-CDF performs significantly better than \name{} ($\alpha=0.05, p=0.02$) when considering Macro AUC. As we compare \name{} to 4 different methods over BioSnap and 3 over Yamanishi dataset, we add a Bonferroni correction by multiplying the $p$-values by 4 and 3, respectively, leading to $p<0.0002$ ($\alpha=0.01$) for all previous comparisons except DTI-CDF. We further run another one-tailed T-test concerning $MicroAUC_p$ with $\alpha=0.01$ including Bonferroni correction. We find that \name{} advances significantly over MolTrans ($p<0.00001$), DeepDTI ($p<0.00001$), DeepDTA ($p<0.00001$), and DeepConv-DTI ($p<0.00001$) regarding BioSnap dataset, and over DTINet ($p<0.00001$), DTIGEMS+ ($p<0.00001$) and DTI-CDF ($p<0.00001$) regarding Yamanishi dataset.

>>>>

As the difference in performance with different splitting schemes is
quite large, we further evaluated additional drug--target interaction
and drug--target affinity prediction methods that were trained and
evaluation on other datasets.  Following the results of MolTrans
\cite{MolTrans2020}, we reevaluated DeepDTI \cite{DeepDTI2017},
DeepDTA \cite{DeepDTA2018}, DeepConv-DTI \cite{DeepConvDTI2019}, and
MolTrans itself on the BioSnap dataset \cite{BioSnap2018} and compared it to our
``na\"ive'' predictor as well as \name{} (see Table
\ref{tab:comparison2}).  MolTrans was evaluated over the drug--target
pair and the protein split; we were able to reproduce the MolTrans
results (Table \ref{tab:comparison2}), showing a substantial
difference based on the splitting scheme. We additionally computed the
$MicroAUC_p$ score for all considered methods, leading to similar 
results as observed on the Yaminishi dataset. As \name{} considers less drugs than alternative approaches, we execute a one-tailed T-test comparing \name{} to all examined methods. Considering Macro AUCs, \name{} improves significantly over MolTrans ($p<10^{-4}$), DeepDTI ($p<10^{-4}$), DeepDTA ($p<10^{-4}$), and DeepConv-DTI ($p<10^{-4}$) with respect to BioSnap dataset, and significantly over DTINet ($p<10^{-4}$) and DTIGEMS+ ($p<10^{-4}$) with respect to Yamanishi dataset. However, DTI-CDF performs significantly better than \name{} ($p=0.02$) when considering Macro AUC. As we compare \name{} to 4 different methods over BioSnap and 3 over Yamanishi dataset, we add a Bonferroni correction by multiplying the $p$-values by 4 and 3, respectively, leading to $p<10^{-3}$ for all previous comparisons except DTI-CDF. We further run another one-tailed T-test concerning $MicroAUC_p$ including Bonferroni correction. We find that \name{} advances significantly over MolTrans ($p<10^{-4}$), DeepDTI ($p<10^{-4}$), DeepDTA ($p<10^{-4}$), and DeepConv-DTI ($p<10^{-4}$) regarding BioSnap dataset, and over DTINet ($p<10^{-4}$), DTIGEMS+ ($p<10^{-4}$) and DTI-CDF ($p<10^{-4}$) regarding Yamanishi dataset.
